A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-02-24 paper/discussion.tex
2 paragraphs in methodology

``Fig. 16.— Updated Determinations of the derived SFR (left axis) and U V
luminosity (right axis) densities versus redshift (5.4). The
left axis gives the SFR densities we would infer from the measured luminosity
densities, assuming the Madau et al. (1998) conversion
factor relevant for star-forming galaxies with ages of 108 yr (see also
Kennicutt 1998). The right axis gives the U V luminosities we infer
integrating the present and published LFs to a faint-end limit of −17 mag (0.03
L∗ )''BOUWENS 2014 UV LF

>>>>

%``Fig. 16.— Updated Determinations of the derived SFR (left axis) and U V
%luminosity (right axis) densities versus redshift (5.4). The
%left axis gives the SFR densities we would infer from the measured luminosity
%densities, assuming the Madau et al. (1998) conversion
%factor relevant for star-forming galaxies with ages of 108 yr (see also
%Kennicutt 1998). The right axis gives the U V luminosities we infer
%integrating the present and published LFs to a faint-end limit of −17 mag (0.03
%L∗ )''BOUWENS 2014 UV LF

### 2015-02-24 paper/draft.tex
2 paragraphs in methodology

\author{F.L. G\'omez-Cort\'es\altaffilmark{1} }
\affil{Departamento de Física, Universidad de los Andes, Colombia}

\begin{abstract}
This work relates baryonic matter and dark matter at redshift $z=5.9$ using 
observational data from CFHTLS \citep{willott13}, HST Legacy Survey
\citep{bouwens14,finkelstein14}, UKIDSS and SDXS \citep{mclure09}, and results of 
the Multidark Simulation \citep{riebe13} in a cubic box of $1000 \textrm{Mpc 
h}^{-1}$ length with 2013 Planck Cosmology. The Luminosity Function (LF) is 
fitted via four parameters with the Markov Chain Monte Carlo method. The 
relationship between the Dark Matter Halos Mass and Star Formation Rate is 
obtained using the relationship between the UV  continuum (from the fitted LF) 
and Star Formation Rate (SFR) by \cite{kennicutt98}.Cosmic variance effects are 
studied on smaller boxes of $250 \textrm{Mpc h}^{-1}$ length.

@@

\include{fitting_model}

\include{star_formation_rate}

\include{observations}

\include{methodology}

@@

\section{Summary}

\acknowledgments
%Gracias Totales
%
\appendix

%\section{Appendix material}
%DEXTER \url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}

\include{the_bibliography}

\end{document}

%%
%% End of file `sample.tex'.

>>>>

\author{Felipe L. G\'omez-Cort\'es\altaffilmark{1} }
\affil{Departamento de F\'isica, Universidad de los Andes, Colombia}

\begin{abstract}
This work relates baryonic matter and dark matter at redshift $z=5.9$ using 
observational data from CFHTLS \citep{willott13}, HST Legacy Survey
\citep{bouwens14,finkelstein14}, UKIDSS and SDXS \citep{mclure09}, and results of 
the Multidark Simulation \citep{klypin14} in a cubic box of $1000 \textrm{Mpc 
h}^{-1}$ length with 2013 Planck Cosmology \citep{planck1}. The Luminosity Function (LF) is 
fitted via four parameters with the Markov Chain Monte Carlo method. The 
relationship between the Dark Matter Halos Mass and Star Formation Rate is 
obtained using the relationship between the UV  continuum (from the fitted LF) 
and Star Formation Rate (SFR) by \cite{kennicutt98}.Cosmic variance effects are 
studied on smaller boxes of $250 \textrm{Mpc h}^{-1}$ length.

@@

\include{observations}
\include{methodology}

@@

%\section{Summary}
\acknowledgments
%Gracias Totales
\appendix
%\section{Appendix material}
\include{the_bibliography}
\end{document}

### 2015-02-24 paper/methodology.tex
2 paragraphs in methodology

The first goal in this paper is reproduce the observed UVLF from DMH, from
 simulations at redshift $z=6$. The observational datasets where aforementioned.

Bolshoi Simulation \citep{riebe13} was performed by the MuldiDark consortium
MultiDark Database is

UV Luminosity as function of DMH mass. 
Parameters.
Dust Extinction

@@

UV luminosity to SFR

>>>>

The key element to connect SFR with halo mass from simulations is the observed UVLF. 
If there exist a function whom gives to each halo a UV luminosity then is posible to 
reproduce UVLF from DMH catalogs. The fitting parameters can be explored using a 
Markov Chain Monte-Carlo (MCMC) implementation. Once the parameters are found, 
the SFR-Halo Mass relation have been found.

We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) Simulation 
\citep{klypin14} with 2013 Planck cosmology \citep{planck1}. MDPL is quite similar to the 
Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{prada12} and 
its predecesor Bolshoi \citep{klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of them with 
WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo catalogs are 
available at the MultiDark Database\footnote{\url{http://www.multidark.org}} 
\citep{riebe13}.

The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side length. 
It has $3840^3$ dark matter particles of 
$1.51\times 9 \textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one.
The 2013 Planck cosmology is defined by the following parameters: $\Sigma_M = 0.307$, 
$\Sigma_B = 0.048$, $\Sigma_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and 
$H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$ 
halos, to avoid incompleteness in the low mass end, halos with mass below 
$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. In order to study how 
cosmic variance can affect measurements, the original catalog is divided into 64 small 
cubic boxes, with a similar volume to the observations.

The following treatment is applied to every one small box.

The halo abundance matching technique has been widely used \citep{colin99, kravtsov04}
resulting in good reproduction of the observed galaxy clustering. \citep{conroy06, lee09}. 
Here we use the simplest case with few premises: 
\begin{enumerate}
 \item Each halo in the catalog hosts one galaxy. There are not empty
halos, also none of halos has two or more galaxies.
 \item The UV luminosity of each galaxy is function of one variable; the mass of
the DMH in which is located. This function must be monotone, this guarantees that most massive halos will host the most luminous galaxies in the same volume.
\end{enumerate}

The simplest relation we can have is a power law, two parametric function:
 \begin{equation}
    L_{\textrm{UV}} (M) = L_0 M^k
 \end{equation}
but it does not reproduce the two slopes in the UVLF.

A better model is a four parameter function. Each galaxy has a luminosity given
by:
  \begin{equation}
  L_{\textrm{UV}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenbosch03} and the mean relation between
stellar mas of a galaxy and the mass of its halo used by \citet{moster10}.

Dust Extinction.

@@

Python, Ipython Notebook, Scipy, Matplotlib, Numpy.

The galaxy UV luminosity can be directly related with SFR according to \citet{madau98}
This model is accurate within the range of $10^8 - 10^9 \textrm{yr}$\citep{kennicutt98}.
The relation between UV luminosity and Star Formation Rate \citep{madau98,kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

### 2015-02-24 paper/the_bibliography.tex
Refs. in observations. Removing intro. Methodology main ideas.
2 paragraphs in methodology

\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53	
		%2006ApJ...653...53B
\bibitem[Bouwens(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
		%2012ApJ...752L...5B
\bibitem[Bouwens et al.(2014)]{bouwens14} Bouwens, R. J., G. D. Illingworth, P. A. Oesch, M. Trenti, I. Labbe', L. Bradley, M. Carollo, et al.2014, arXiv:1403.4295

\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 
36, 189		%1998ARA&A..36..189K
\bibitem[Kennicutt(2009)]{kennicutt09} Kennicutt, Robert C., Jr et al. 2009, \apj, 
703, 4672	%2009ApJ...703.1672K
\bibitem[Law(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
		%2011ApJ...738..124L
\bibitem[Jiang(2011)]{jiang11} Jiang, Linhua et al. 2011, \apj, 743, 65
		%2011ApJ...743...65J
\bibitem[Lee(2009)]{lee09} Lee, Kyoung-Soo et al. 2009, \apj, 695, 368
		%2009ApJ...695..368L
\bibitem[Lundgren(2014]{lundgren14} Lundgren, Britt F. et al, 2014, \apj, 780,
34		%2014ApJ...780...34L
\bibitem[Madau(1998)]{madau98} Madau, Piero. et al, 1998, \apj, 498, 106M
		%1998ApJ...498..106M
\bibitem[McLure et al.(2009)]{mclure09} McLure, R. J., M. Cirasuolo, J. S. Dunlop, S. Foucaud, \and O. Almaini. 2009, \mnras, 395, 2196	
		%2009MNRAS.395.2196M
\bibitem[Moster(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
903 
\bibitem[Riebe(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 		
		%2013AN....334..691R
\bibitem[Steidel(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 
728 		%2003ApJ...592..728S
\bibitem[Trimble(1987)]{trimble87} Trible, Virginia. 1987, \araa, 25, 425

\bibitem[van den Bosch(203)]{vandenbosch03} van den Bosh, Frank C. et al. 2003, \mnras,
40, 771		%2003MNRAS.340..771V
\bibitem[Willott et al.(2013)]{willott13} Willott, Chris J., Ross J. McLure, Pascale Hibon, Richard Bielby, Henry J. McCracken, Jean-Paul Kneib, Olivier Ilbert, David G. Bonfield, Victoria A. Bruce, \and Matt J. Jarvis. 2013, \aj, 145, 4	
		%2013AJ....145....4W
\end{thebibliography}

>>>>

\bibitem[Behroozi et al.(2013)]{behroozi13} Behroozi, Peter S., Risa H. Wechsler, 
\and Charlie Conroy. 2013, \apj,  770, 57
% Semi-Analytical Model for SFR-DMHM

\bibitem[Bouwens et al.(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53	
		%2006ApJ...653...53B
% Observational luminosity function

\bibitem[Bouwens et al.(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
		%2012ApJ...752L...5B
% Observational luminosity function

\bibitem[Bouwens et al.(2014)]{bouwens14} Bouwens, R. J., G. D. Illingworth, P. A. 
Oesch, M. Trenti, I. Labbe', L. Bradley, M. Carollo, et al. 2014, arXiv:1403.4295
% Observational luminosity function

\bibitem[Col\'in et al.(1999)]{colin99}
Col\'n, Pedro, Anatoly A. Klypin, Andrey V. Kravtsov, and Alexei M. Khokhlov. 
1999, \apj , 523,32
% Halo Abundance Matching
\bibitem[Conroy et al.(2006)]{conroy06}
Conroy, Charlie, Risa H. Wechsler, \and Andrey V. Kravtsov. 2006, \apj,647,201
% Halo Abundance Matching

\bibitem[Efstathiou et al.(1988)]{efstathiou88} Efstathiou, G., Richard S. Ellis, 
\and Bruce A. Peterson. 1988, \mnras, 232,431.
% StepWise Maximun Likelihood LF

\bibitem[Finkelstein et al.(2014)]{finkelstein14} Finkelstein, Steven L., Russell E. 
Ryan Jr., Casey Papovich, Mark Dickinson, Mimi Song, Rachel Somerville, 
Henry C. Ferguson, et al. 2014, arXiv:1410.5439
% Observational luminosity function

\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 
36, 189		%1998ARA&A..36..189K
\bibitem[Kennicutt et al.(2009)]{kennicutt09} Kennicutt, Robert C., Jr et al. 2009, \apj, 
703, 4672	%2009ApJ...703.1672K

\bibitem[Kravtsov et al.(2004)]{kravtsov04}
Kravtsov, Andrey V., Andreas A. Berlind, Risa H. Wechsler, Anatoly A. Klypin, 
Stefan Gottlöber, Brandon Allgood, \and Joel R. Primack. 2004, \apj, 609, 35
%Halo Abundance Matching

\bibitem[Klypin et al.(2011)]{klypin11} Klypin, Anatoly A., Sebastian Trujillo-Gomez, \
and Joel Primack. 2009, \apj, 740, 102
% Bolshoi 2011

\bibitem[Klypin et al.(2014)]{klypin14} Anatoly Klypin, Gustavo Yepes, Stefan Gottlober, 
Francisco Prada \and Steffen Hess. 2014, arXiv:`1411.4001
% Big Bolshoi Planck 1 - MDPL

\bibitem[Law et al.(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
		%2011ApJ...738..124L
\bibitem[Jiang et al.(2011)]{jiang11} Jiang, Linhua et al. 2011, \apj, 743, 65
		%2011ApJ...743...65J
\bibitem[Lee et al.(2009)]{lee09} Lee, Kyoung-Soo et al. 2009, \apj, 695, 368
		%2009ApJ...695..368L
\bibitem[Lundgren et al.(2014]{lundgren14} Lundgren, Britt F. et al, 2014, \apj, 780,
34		%2014ApJ...780...34L
\bibitem[Madau et al.(1998)]{madau98} Madau, Piero. et al, 1998, \apj, 498, 106M
		%1998ApJ...498..106M
\bibitem[McLure et al.(2009)]{mclure09} McLure, R. J., M. Cirasuolo, J. S. Dunlop, S. Foucaud, \and O. Almaini. 2009, \mnras, 395, 2196	
		%2009MNRAS.395.2196M
\bibitem[Moster et al.(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
903

\bibitem[Planck Collaboration et al(2014)]{planck1}
Planck Collaboration, P. A. R. Ade, N. Aghanim, C. Armitage-Caplan, M. Arnaud, 
M. Ashdown, F. Atrio-Barandela, et al. \aap, 571, A16
%Planck 2013 cosmology release.

\bibitem[Prada et al.(2012)]{prada12} Prada, Francisco, Anatoly A. Klypin, 
Antonio J. Cuesta, Juan E. Betancort-Rijo, and Joel Primack. 2012. \mnras, 423, 3018
% Big Bolshoi

\bibitem[Riebe et al.(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 		
% Multiyear Database Release		%2013AN....334..691R

\bibitem[Schmidt(1968)]{schmidt68} Schmidt, Maarten. 1968, \apj 151, 393.
% StepWise Maximun Likelihood LF

\bibitem[Steidel et al.(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 
728 		%2003ApJ...592..728S
\bibitem[Trimble(1987)]{trimble87} Trible, Virginia. 1987, \araa, 25, 425

\bibitem[van den Bosch et al.(203)]{vandenbosch03} van den Bosh, Frank C. et al. 2003, \mnras,
40, 771		%2003MNRAS.340..771V

\bibitem[Willott et al.(2013)]{willott13} Willott, Chris J., Ross J. McLure, Pascale Hibon,
 Richard Bielby, Henry J. McCracken, Jean-Paul Kneib, Olivier Ilbert, David G. Bonfield,
  Victoria A. Bruce, \and Matt J. Jarvis. 2013, \aj, 145, 4	
		%2013AJ....145....4W
\end{thebibliography}
